Master thesis problem statement: Keyword search over heterogeneous sources

### 2012-10-18 doc/thesis/latex/proposed_solutions.tex
slight modifications to report

\item Given a keyword query, suggest the best matching structured queries (as a ranked list)%
 	\footnote{As DAS uses Boolean IR model we could only rank specific structured queries, but not the results itself.}:
	\begin{itemize}
	\item the algorithm will generate mappings between each keyword to either an entity name, selection attribute name or its value (resembling 'Query forms' and 'Keyword cleaning' approaches)
	\item ranking could be based on: how closely keywords are matching (some or all) required API's input parameters, popularity of certain queries and users feedback	
	\item build an inverted index of attribute values with some good full-text search toolkit%
				\footnote{e.g. Xapian (http://xapian.org/) implemented in C++ which that is known for its flexibility, or Sphinx (http://sphinxsearch.com/)}. 
	If no match found (e.g. new entry not yet in our cache) pattern matching could be used to make a best guess
	\item the system could improve its results from users' feedback (e.g. by HMM, will need to decide)
	\item multi-wildcard queries (e.g. dataset=*Zmm*special*RECO*) are common at CMS that will need special attention\footnote{Matching to structured query will be harder and guessing even worse. Also for performance reasons some web-services will introduce limitations on the format of wilcard queries, while DAS wants still to be flexible at least for datasets}.

>>>>

\item Given a keyword query, suggest the best matching structured queries (as a ranked list)%
 	\footnote{As DAS uses Boolean IR model we could only rank specific structured queries, but not the results itself.}:
	\begin{itemize}
	\item the algorithm will generate mappings between each keyword to either an entity name, selection attribute name or its value (resembling 'Query forms' and 'Keyword cleaning' approaches)
	\item ranking could be based on: how closely keywords are matching (some or all) required API's input parameters, popularity of certain queries, users' feedback	 and user's personal profile (e.g. search history, department, etc)
	\item build an inverted index of attribute values with some good full-text search toolkit%
				\footnote{e.g. Xapian (http://xapian.org/) implemented in C++ which that is known for its flexibility, or Sphinx (http://sphinxsearch.com/)}. 
	If no match found (e.g. new entry not yet in our cache) pattern matching could be used to make a best guess
	\item the system could improve its results from users' feedback (e.g. by HMM, will need to decide)
	\item multi-wildcard queries (e.g. dataset=*Zmm*special*RECO*) are common at CMS that will need special attention\footnote{Matching to structured query will be harder and guessing even worse. Also for performance reasons some web-services will introduce limitations on the format of wilcard queries, while DAS wants still to be flexible at least for datasets}.

### 2012-10-18 doc/thesis/latex/report_sept.tex
slight modifications to report

% enable Hyperlinks
\usepackage{hyperref}
% fancy verbatim
\usepackage{fancyvrb}
\usepackage{appendix}

@@

\subsection{Generic connector accessing relational databases}
{\color{red}Generic connector able to access relational databases with minimal manual integration could be useful for integrating proprietary systems that were not yet integrated and there's no resources available to build APIs. A possible use-case could be the \textit{Prep} database, but this still has to be discussed. 
%
Depending on the needs it could be either of exploratory or API/Query Forms based approach, where fake APIs are defined in terms of SQL queries (or even better in a simplified form that would generate SQL by taking schema into account)}
{
There was a project\footnote{\url{https://github.com/vkuznet/PyQueryBuilder}}   at CERN which tried to generalize DBS-Query Language for any database.}

>>>>

% enable Hyperlinks
\usepackage{hyperref}
% fancy verbatim
\usepackage{fancyvrb}
\usepackage{appendix}
\usepackage[usenames,dvipsnames]{xcolor}

@@

{\color{gray}
\subsection{Generic connector accessing relational databases}
Generic connector able to access relational databases with minimal manual integration could be useful for integrating proprietary systems that were not yet integrated and there's no resources available to build APIs. A possible use-case could be the \textit{Prep} database, but this still has to be discussed. 
%
Depending on the needs it could be either of exploratory or API/Query Forms based approach, where fake APIs are defined in terms of SQL queries (or even better in a simplified form that would generate SQL by taking schema into account).
There was a project\footnote{\url{https://github.com/vkuznet/PyQueryBuilder}}   at CERN which tried to generalize DBS-Query Language for any database that could be used for this.}
